### 2025-07-21 paper/quarto_aaai/paper.tex
adjsutments to remove Quarto generated latex

\small
\centering
\input{tables/main.tex}

@@

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\renewcommand{\bibsection}{}
\bibliography{../quarto_aaai/bibliography.bib}
\end{document}

>>>>

\small
\centering
\begin{tabular}{
  l
  S[table-format=2.2(1.2)]
  S[table-format=3.2(3.2)]
  S[table-format=3.2(1.2)]
}
  \toprule
  \textbf{Data} & \textbf{$ \text{IP} $ $(-\%)$} & \textbf{$ \text{IP}^* $ $(-\%)$} & \textbf{Cost $(-\%)$} \\\midrule
  LS & 29.05\pm0.67 $^{*}$ & 55.33\pm2.03 $^{*}$ & 14.07\pm0.6 $^{*}$ \\
  Circ & 56.29\pm0.44 $^{*}$ & 89.38\pm9.3 $^{*}$ & 45.55\pm0.76 $^{*}$ \\
  Moon & 20.62\pm0.69 $^{*}$ & 19.26\pm8.12 $^{*}$ & 2.86\pm1.03 $^{*}$ \\
  OL & -1.13\pm0.88 $^{}$ & -24.52\pm14.52 $^{}$ & 38.39\pm2.21 $^{*}$ \\\midrule
  Adult & 0.77\pm1.34 $^{}$ & 32.29\pm6.87 $^{*}$ & -2.82\pm4.88 $^{}$ \\
  CH & 12.05\pm1.41 $^{*}$ & 70.27\pm3.72 $^{*}$ & 40.71\pm1.55 $^{*}$ \\
  Cred & 12.31\pm1.84 $^{*}$ & 54.89\pm11.21 $^{*}$ & -17.43\pm5.17 $^{*}$ \\
  GMSC & 23.44\pm1.99 $^{*}$ & 73.31\pm4.83 $^{*}$ & 62.64\pm2.04 $^{*}$ \\
  MNIST & 7.05\pm1.8 $^{*}$ & -25.09\pm109.05 $^{}$ & -12.34\pm6.52 $^{}$ \\\midrule
  Avg. & 17.83 & 38.35 & 19.07 \\\bottomrule
\end{tabular}

@@

\bibliography{../quarto_aaai/bibliography.bib}
\end{document}

### 2025-07-21 paper/sections/experiments.qmd
adjsutments to remove Quarto generated latex

::: {#tbl-main}
```{=latex}
\begin{table}[h]
\small
\centering
\input{tables/main.tex}
\end{table}
```
Key evaluation metrics for valid counterfactual along with bootstrapped standard errors for all datasets. **Plausibility** (columns 1-2): percentage reduction in implausibility for $\text{IP}$ and $\text{IP}^*$, respectively; **Cost** / **Actionability** (column 3): percentage reduction in costs when selected features are protected. Outcomes are aggregated across bootstrap samples and varying degrees of the energy penalty $\lambda_{\text{egy}}$ used for *ECCCo* at test time. Asterisks ($^*$) indicate that the bootstrapped 99%-confidence interval of differences in mean outcomes does *not* include zero.
:::

>>>>

::: {#tbl-main}
```{=latex}
\begin{table}[h]
\small
\centering
\begin{tabular}{
  l
  S[table-format=2.2(1.2)]
  S[table-format=3.2(3.2)]
  S[table-format=3.2(1.2)]
}
  \toprule
  \textbf{Data} & \textbf{$ \text{IP} $ $(-\%)$} & \textbf{$ \text{IP}^* $ $(-\%)$} & \textbf{Cost $(-\%)$} \\\midrule
  LS & 29.05\pm0.67 $^{*}$ & 55.33\pm2.03 $^{*}$ & 14.07\pm0.6 $^{*}$ \\
  Circ & 56.29\pm0.44 $^{*}$ & 89.38\pm9.3 $^{*}$ & 45.55\pm0.76 $^{*}$ \\
  Moon & 20.62\pm0.69 $^{*}$ & 19.26\pm8.12 $^{*}$ & 2.86\pm1.03 $^{*}$ \\
  OL & -1.13\pm0.88 $^{}$ & -24.52\pm14.52 $^{}$ & 38.39\pm2.21 $^{*}$ \\\midrule
  Adult & 0.77\pm1.34 $^{}$ & 32.29\pm6.87 $^{*}$ & -2.82\pm4.88 $^{}$ \\
  CH & 12.05\pm1.41 $^{*}$ & 70.27\pm3.72 $^{*}$ & 40.71\pm1.55 $^{*}$ \\
  Cred & 12.31\pm1.84 $^{*}$ & 54.89\pm11.21 $^{*}$ & -17.43\pm5.17 $^{*}$ \\
  GMSC & 23.44\pm1.99 $^{*}$ & 73.31\pm4.83 $^{*}$ & 62.64\pm2.04 $^{*}$ \\
  MNIST & 7.05\pm1.8 $^{*}$ & -25.09\pm109.05 $^{}$ & -12.34\pm6.52 $^{}$ \\\midrule
  Avg. & 17.83 & 38.35 & 19.07 \\\bottomrule
\end{tabular}
\end{table}
```
Key evaluation metrics for valid counterfactual along with bootstrapped standard errors for all datasets. **Plausibility** (columns 1-2): percentage reduction in implausibility for $\text{IP}$ and $\text{IP}^*$, respectively; **Cost** / **Actionability** (column 3): percentage reduction in costs when selected features are protected. Outcomes are aggregated across bootstrap samples and varying degrees of the energy penalty $\lambda_{\text{egy}}$ used for *ECCCo* at test time. Asterisks ($^*$) indicate that the bootstrapped 99%-confidence interval of differences in mean outcomes does *not* include zero.
:::
